### 2015-09-10 draft.tex
...
...

\documentclass[11pt]{article} 
\usepackage[american]{babel}
\usepackage{makeidx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{subcaption}

@@

\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[proposition]
\newcommand{\pr}{{\rm Pr}}
\newcommand{\e}{{\rm E}}

@@

\begin{center} 
\Large {Tel-Aviv University}

\Large {The Raymond and Beverly Sackler Faculty of} \\
\Large {Exact Sciences} \\
\Large {The Department of Statistics and Operations} \\
\Large {Research}

\bigskip
\bigskip
\bigskip

\Large {\bf Draft }

\bigskip
\bigskip
\bigskip
\bigskip

\Large{Thesis Submitted Towards the Degree of Master} \\
\Large {of Science in Operations Research}

\bigskip

\Large {Ran Snitkovsky}

\bigskip
\bigskip
\bigskip

\Large {Supervisor:} \\
\Large {Prof. Refael Hassin}

\bigskip
\bigskip

\Large{2014}

\end{center}

\begin{center} \Large {\bf Draft}
\end{center}

@@

To-do...

@@

To-do...

@@

We consider a system composed of two identical servers, $S_{1}$ and $S_{2}$, each one's service-duration is exponential with rate $\mu$, and a single FCFS unobservable queue (see Fig.\ref{CostumersFlow}). Costumers are identical, and arrive at the system following a Poisson-process with rate $\Lambda$. Upon arrival, a costumer chooses one of two options: pay a {\it sensing-price} and try to attain service in $S_{2}$ (a.k.a, {\it Sense}), or join the queue and wait until accepted to service in $S_{1}$ (a.k.a {\it Not-Sense}). A costumer who chooses to sense $S_{2}$ and finds it idle is immediately accepted to service without waiting. However, if he finds $S_{2}$ occupied, he is sent to the queue and waits his turn to service by $S_{1}$.

Denote $p$ the probability that a costumer senses $S_{2}$, and denote $(X_{1}(t), X_{2}(t))$ the state of the system at time $t$, consisting of the number of costumers in the queue (including the one in service at $S_{1}$) and the state of $S_{2}$ respectively, with $X_{1}(t) \in \lbrace0, 1, 2, \ldots\rbrace$ and $X_{2}(t) \in \lbrace0, 1\rbrace$ (0 means that $S_{2}$ is idle). Thus, the system can be described as a bi-dimensional Markov process, as shown in Fig.\ref{MarkovChain}, and the stationary probabilities are computed through the following set of equations:

@@

\begin{equation}
  \forall n \in \lbrace 1, 2, \ldots \rbrace: \ \begin{cases}
    (\mu+\Lambda) P_{n,0} - (1-p) \Lambda P_{n-1, 0} - \mu P_{n+1,0}  - \mu P_{n,1} = 0\:,\\
    (2\mu+\Lambda) P_{n,1} - p\Lambda P_{n,0}  - \Lambda P_{n-1,1} - \mu P_{n+1,1} = 0\:.
  \end{cases} \label{StateEq2}
\end{equation}
where $P_{i,j}$ is the stationary probability that the system is in state $(i,j)$. These equations induce the following relationship:

@@

By the assumption that each individual chooses randomly and independently whether or not to sense, we deduce that the sub-system $S_{2}$ can be considered as an M/M/1/1 queue (Erlang's Loss Model) with arrival rate $p\Lambda$ and service rate $\mu$. Therefore, the {\it loss-probability} of $S_{2}$ (i.e., the probability that a costumer sensing $S_{2}$ will find it occupied) is:
\begin{equation}
	\pr(X_2=1) = \sum\limits_{i=0}^{\infty} P_{i, 1} = \dfrac{p\Lambda}{\mu+p\Lambda}\:, \label{LossProb}
\end{equation}
and its complement:
\begin{equation}
	\pr(X_2=0) = 1-\pr(X_2=1) = \sum\limits_{i=0}^{\infty} P_{i, 0} = \dfrac{\mu}{\mu+p\Lambda}\:. \label{OMLossProb}
\end{equation}
One can also derive the above formula by summing the right-hand-sides of the equations in (\ref{RecurtionRule}) for $n=0,1,2,\ldots$ and equating the sum of this infinite series to $1-(P_{0,0}+P_{0,1})$, considering that in steady state of the system: \[ p\Lambda\sum_{i=0}^{\infty}P_{i,0} - \mu \sum_{i=0}^{\infty}P_{i,1} = 0\:.\]

Summing the equations in (\ref{RecurtionRule}) for $n=0,1,2,\ldots$ and substituting (\ref{LossProb}) and (\ref{OMLossProb}) we get:

@@

Subtracting the second equation from the first one in (\ref{StateEq2}) and combining with (\ref{RecurtionRule}) we deduce the following formulae:
\begin{equation}
	\forall n \in \lbrace 0, 1, \ldots \rbrace: \
  	\begin{cases}
    	P_{n+1,0} = (1-p) \frac{\Lambda}{\mu} P_{n, 0} + p \frac{\Lambda}{\mu} \sum\limits_{i=0}^{n}P_{i,0} - \sum\limits_{i=0}^{n}P_{i,1}\\
   	 	P_{n+1,1} = \frac{\Lambda}{\mu} P_{n, 1} + \sum\limits_{i=0}^{n}P_{i,1} - p \frac{\Lambda}{\mu} \sum\limits_{i=0}^{n}P_{i,0}
  	\end{cases} \label{Forms}
\end{equation}
It can be seen from (\ref{Forms}) that, for given constants $p$ and $\sfrac{\Lambda}{\mu}$, every value $P_{n+1,k}$ ($k\in\lbrace0,1\rbrace$) is expressed as a linear combination of $\lbrace P_{n,0}, P_{n-1,0}, \ldots, P_{0,0}, P_{n,1}, P_{n-1,1}, \ldots, P_{0,1},  \rbrace$. Hence, with (\ref{P00PlusP01}), it follows by induction that for each $n \in \lbrace 0, 1, \ldots \rbrace$ and for each $k \in \lbrace 0, 1 \rbrace$, $P_{n,k}$ is a linear function of $P_{0,0}$, as a countable sum of linear functions. Thus, for $N$ sufficiently large, one can bound the queue length by $N$, express the finite series $\sum_{i=0}^{N} P_{i,0}+P_{i,1}$ as a linear function of $P_{0,0}$, equate to 1 and find a fixed value of $P_{0,0}$ (and all other $P_{n,k}$) in $O(N)$ time complexity.
\newpage

\section{System-utilization}
We now intend to find the maximum utilization of the system. For convenience we use the notation $\rho:=\sfrac{\Lambda}{\mu}$. The {\it effective-arrival-rate} to the queue, $\tilde{\lambda}(p,\rho)$, consists of two streams of arrivals: costumers who join the queue without sensing at all (whose proportion is $1-p$) and costumers who sense $S_{2}$ and find it busy (whose proportion is $p \cdot \pr(X_2=1)$). Therefore,
\[ \tilde{\lambda}(p,\rho) = (1-p)\Lambda + \pr(X_2=1)\cdot p \Lambda\:. \]
Substituting (\ref{LossProb}) and dividing by $\mu$ we get the {\it effective-utilization}, $\tilde{\rho}(p,\rho)$:
\begin{equation}
\tilde{\rho}(p,\rho) := \frac{1}{\mu}\tilde{\lambda}(p,\rho) = \rho - \frac{1}{1+p\rho}p\rho\:, \label{EffectiveUtil}
\end{equation}
which is monotone decreasing in $p$ for every $\rho\in(0,\infty)$.

The stochastic process representing the stream of arrivals over time to the queue served by $S_{1}$ is not poissonian. This is because the inter-arrival times to the queue are not i.i.d., and the arrival-rate increases when $S_2$ is busy in comparison to the arrival-rate in its idle periods. Thus, we model this sub-system as a G/M/1 with possibly dependent inter-arrival times, and for the system to remain stable we assume $\tilde{\rho}(p,\rho) < 1$.

@@

\begin{proposition}
For each $\rho\in(0,\varphi)$, there exists a lower bound for $p$, denoted $\underline{p}$, such that for every $p \in (\underline{p}, 1]$ the system is stable.
\end{proposition}

\begin{proof}
As discussed, a stable system must satisfy: $\tilde{\rho}(p,\rho) < 1$. Substitute (\ref{EffectiveUtil}) and isolate $p$ in the inequality to get an equivalent stability criterion:
\[ p > \frac{\rho - 1}{\rho(\rho-2)} =: \underline{p}\]
from which it is clear that, given a value $\rho$, the system is stable for all $p \in (\underline{p},1]$.

Finding the maximum throughput we assume that $p=1$, which means everyone try to attain service in $S_{2}$ before they join the queue. This is followed by the monotonicity of $\tilde{\rho}(p,\rho)$. Then, from (\ref{EffectiveUtil}), the stability criterion is:
\[ \tilde{\rho}(1,\rho)=\frac{\rho^2}{1+\rho}<1 \quad\Leftrightarrow\quad \rho^2-\rho-1<0 \quad\Leftrightarrow\quad \rho < \frac{1+\sqrt{5}}{2}=\varphi \]
where $\varphi$ is the well-studied golden ratio, concluding that for every $\rho\in(0,\varphi)$ and $p \in (\underline{p},1]$, the system is stable.
\end{proof}

\newpage
\section{Equilibrium Strategy}
In this section we discuss the states and (Nash) equilibrium strategies in the system. Let $c_{w}>0$ be the waiting cost per unit time of an individual costumer waiting in line, and $c_{s}>0$ be the cost of sensing (incurred by each costumer who chooses to sense, regardless of the consequences of his action). Since all costumers are identical, and each one arriving at the system is eventually attained to service, neither the reward from service nor the time spent in service is relevant. Of course, the state of the system, including the length of the queue and the status of the servers, is unobservable as mentioned, and unknown to the costumers at the time they make their decisions. We assume the system is not overloaded (i.e., $\rho<\varphi$) and that all costumers act to reduce their expected cost to minimum. Denote $C_{S}(p)$ and $C_{N}(p)$ the expected cost of an individual who chooses to sense and an individual who chooses not to sense, respectively, given that the others' probability of sensing is $p$.
\begin{equation}\begin{cases}
 	C_{N}(p) = \frac{c_{w}}{\mu}\e\left[L(p)\right] \\
	C_{S}(p) = c_{s} + \pr(X_2=1) \cdot \frac{c_{w}}{\mu} \e\left[L(p)\mid X_{2}=1\right] 
\end{cases}
\label{LossFunc}
\end{equation}
where $L(p)$ is a random variable representing the observed queue length (including the costumer in service) upon arrival to the system, with $p$ the proportion of the population that sense.

\begin{proposition}
The function $\e\left[L(p)\mid X_2=0\right]$ is continuous and monotone non-increasing in $p$. \label{MonotonicityProp}
\end{proposition}

\begin{proof}
To-do...
\end{proof}

>>>>

\documentclass[11pt]{article} 
\usepackage[american]{babel}
\usepackage{makeidx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{xfrac}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{enumerate}
\usepackage{enumitem}

@@

\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[proposition]
\newcommand{\pr}{{\rm Pr}}
\newcommand{\e}{{\rm E}}
\newcommand{\expdist}{{\rm exp}}
\newcommand{\U}{{\rm U}}
\DeclareMathOperator*{\argmin}{arg\,min}

@@

\begin{center} \Large {\bf Strategic Sensing in Cognitive Radio Networks}
\end{center}

@@

We study a noncooperative multi-player game problem of individual rational users sending data-packets (``customers'' in the terminology of queueing theory) in a Cognitive Radio Network (CRN) with the opportunity of spectrum sensing. The system is composed of two channels (or ``servers''): One unlicensed channel shared freely among all users, and one in which the transmission entails the cost of sensing, and can be denied if the channel is already occupied. It is the users' prerogative to decide whether to use the shared channel or sense, hopefully not encountering a rejection. If a denied customer leaves never to return, the system can be analyzed as two independent subsystems with poissonian stream of arrivals to each one, an M/M/1/1 and an M/M/1, and it can be easily shown that that there exists a unique Nash equilibrium. As opposed to such simple models, in our model customers that are rejected from service after sensing are routed to the shared queue. We model this process as a queueing system comprising of two servers working in parallel, one is an M/M/1/1 loss system and the other is a G/M/1 with heterogeneous arrivals. We compute the transition probabilities and the stationary probabilities of the Markov chain describing the process, analyze the system's capacity and utilization and show, using the technique of Sample Path Analysis, that the Nash equilibrium strategy in the system is well-defined.

@@

@@

We consider a system composed of two identical servers, $S_Q$ and $S_L$ (Q for queue, L for loss), each one's service-duration is exponential with rate $\mu$, and a single FCFS unobservable queue (see Fig.\ref{CustomersFlow}). Customers are identical, and arrive at the system following a Poisson process with rate $\Lambda$. Upon arrival, a costumer chooses one of two options: pay a {\it sensing price} and try to attain service in $S_L$ (a.k.a, {\it Sense}), or join the queue and wait until accepted to service in $S_Q$. A costumer who chooses to sense $S_L$ and finds it idle is immediately accepted to service without waiting. If he/she finds $S_L$ occupied, he/she is sent to the queue and waits his/her turn to service by $S_Q$.

Denote $p$ the probability that a costumer senses $S_L$, and denote $(X(t), Y(t))$ the state of the system at time $t$, consisting of $X(t) \in \lbrace0, 1, 2, \ldots\rbrace$ the number of customers in the queue (including the one in service at $S_Q$), and $Y(t) \in \lbrace0, 1\rbrace$ the state of $S_L$ (where $Y(t)=0$ means that $S_L$ is idle at time $t$). Thus, the system can be described as a bi-dimensional Markov process, as shown in Fig.\ref{MarkovChain}, and the stationary probabilities are computed through the following set of equations:

@@

\begin{equation}
  \forall n \in \lbrace 1, 2, \ldots \rbrace: \ \begin{cases}
    (\mu+\Lambda) P_{n,0} - (1-p) \Lambda P_{n-1, 0} - \mu P_{n+1,0}  - \mu P_{n,1} = 0\:,\\
    (2\mu+\Lambda) P_{n,1} - p\Lambda P_{n,0}  - \Lambda P_{n-1,1} - \mu P_{n+1,1} = 0\:.
  \end{cases} \label{StateEq2}
\end{equation}
where $P_{i,j}$ is the stationary probability that the system is in state $(i,j)$. These equations lead to the following relationship:

@@

By the assumption that each individual chooses randomly and independently whether or not to sense, we deduce that the sub-system $S_L$ can be considered as an M/M/1/1 queue (Erlang's Loss Model) with arrival rate $p\Lambda$ and service rate $\mu$. Therefore, the {\it loss-probability} of $S_L$ (i.e., the probability that a customer sensing $S_L$ will find it occupied) is:
\begin{equation}
	\pr(Y=1) = \sum\limits_{i=0}^{\infty} P_{i, 1} = \dfrac{p\Lambda}{\mu+p\Lambda}\:, \label{LossProb}
\end{equation}
and its complement:
\begin{equation}
	\pr(Y=0) = 1-\pr(Y=1) = \sum\limits_{i=0}^{\infty} P_{i, 0} = \dfrac{\mu}{\mu+p\Lambda}\:. \label{OMLossProb}
\end{equation}
One can also derive the above formula by summing the right-hand-sides of the equations in (\ref{RecurtionRule}) for $n=0,1,2,\ldots$ and equating the sum of this infinite series to $1-(P_{0,0}+P_{0,1})$, considering that in steady state of the system: \[ p\Lambda\sum_{i=0}^{\infty}P_{i,0} - \mu \sum_{i=0}^{\infty}P_{i,1} = 0\:.\]

Summing the equations in (\ref{RecurtionRule}) for $n=0,1,2,\ldots$ and utilizing (\ref{LossProb}) and (\ref{OMLossProb}) we get:

@@

Subtracting the second equation from the first one in (\ref{StateEq2}) and combining with (\ref{RecurtionRule}) we deduce the following formulae:
\begin{equation}
	\forall n \in \lbrace 0, 1, \ldots \rbrace: \
  	\begin{cases}
    	P_{n+1,0} = (1-p) \frac{\Lambda}{\mu} P_{n, 0} + p \frac{\Lambda}{\mu} \sum\limits_{i=0}^{n}P_{i,0} - \sum\limits_{i=0}^{n}P_{i,1}\:, \\
   	 	P_{n+1,1} = \frac{\Lambda}{\mu} P_{n, 1} + \sum\limits_{i=0}^{n}P_{i,1} - p \frac{\Lambda}{\mu} \sum\limits_{i=0}^{n}P_{i,0} \:.
  	\end{cases} \label{Forms}
\end{equation}
It can be seen from (\ref{Forms}) that, for given constants $p$ and $\sfrac{\Lambda}{\mu}$, every value $P_{n+1,k}$ ($k\in\lbrace0,1\rbrace$) is expressed as a linear combination of $\lbrace P_{0,0}, P_{1,0}, \ldots, P_{n,0}, P_{0,1}, P_{1,1}, \ldots, P_{n,1}  \rbrace$. Hence, with (\ref{P00PlusP01}), it follows by induction that for each $n \in \lbrace 0, 1, \ldots \rbrace$ and for each $k \in \lbrace 0, 1 \rbrace$, $P_{n,k}$ is a linear function of $P_{0,0}$, as a countable sum of linear functions. Thus, for $N$ sufficiently large, one can bound the queue length by $N$, express the finite series $\sum_{i=0}^{N} P_{i,0}+P_{i,1}$ as a linear function of $P_{0,0}$, equate to 1 and find a fixed value of $P_{0,0}$ (and all other $P_{n,k}$) in $O(N)$ time complexity.
\newpage

\section{System-utilization}
We now intend to find the maximum utilization of the system. For convenience we use the notation $\rho:=\sfrac{\Lambda}{\mu}$. The {\it effective-arrival-rate} to the queue, $\hat{\lambda}(p,\rho)$, consists of two streams of arrivals: customers who join the queue without sensing at all (whose proportion is $1-p$) and customers who sense $S_L$ and find it busy (whose proportion is $p \cdot \pr(Y=1)$). Therefore,
\[ \hat{\lambda}(p,\rho) = (1-p)\Lambda + \pr(Y=1)\cdot p \Lambda \:. \]
Using (\ref{LossProb}) and dividing by $\mu$ we get the {\it effective-utilization}, $\hat{\rho}(p,\rho)$:
\begin{equation}
\hat{\rho}(p,\rho) := \frac{1}{\mu}\hat{\lambda}(p,\rho) = \rho - p\rho + \frac{p\rho}{1+p\rho}p\rho = \rho - \frac{1}{1+p\rho}p\rho\:, \label{EffectiveUtil}
\end{equation}
which is monotone decreasing in $p$ for every $\rho\in(0,\infty)$.

Note, by (\ref{P00PlusP01}), that $\hat{\rho}(p,\rho)$ is equal to $1-(P_{0,0}+P_{0,1})$, for it represents the {\it busy fraction} of subsystem $S_Q$.

The stochastic process representing the stream of arrivals over time to the queue served by $S_Q$ is not necessarily poissonian. This is because the inter-arrival times to the queue for $p \neq 0$ are not i.i.d., and the arrival-rate increases when $S_L$ is busy in comparison to the arrival-rate in its idle periods. Thus, we model this subsystem as a G/M/1 with heterogeneous inter-arrival times, and for the system to remain stable, as implied by \cite{Yehiali&Naor}, we assume $\hat{\rho}(p,\rho) < 1$.

@@

\begin{proposition}
For each $\rho\in(0,\varphi)$, there exists a lower bound for $p$, denoted $\underline{p}$, such that the system is stable iff $p \in (\underline{p}, 1]$.
\end{proposition}

\begin{proof}
As discussed, a necessary and sufficient condition for stability is: $\hat{\rho}(p,\rho) < 1$. Substitute (\ref{EffectiveUtil}) and isolate $p$ in the inequality to get an equivalent stability criterion:
\[ p > \frac{\rho - 1}{\rho(2-\rho)} =: \underline{p}\]
from which it is clear that, if the system is stable for some $p_0 > \underline{p}$, it is also stable for all $p \in [p_0,1]$.

Finding the maximum throughput we assume that $p=1$, which means everyone senses $S_L$ before they join the queue. This is followed by the monotonicity of $\hat{\rho}(p,\rho)$. Then, from (\ref{EffectiveUtil}), the stability criterion is:
\[ \hat{\rho}(1,\rho)=\frac{\rho^2}{1+\rho}<1 \quad\Leftrightarrow\quad \rho^2-\rho-1<0 \quad\Leftrightarrow\quad \rho < \frac{1+\sqrt{5}}{2}=\varphi \]
where $\varphi$ is the golden ratio, concluding that for every $\rho\in(0,\varphi)$ and $p \in (\underline{p},1]$, the system is stable.
\end{proof}

\newpage
\section{Equilibrium Strategy}
In this section we discuss the states and (Nash) equilibrium strategies in the system. Let $c_{w}>0$ be the waiting cost per unit time of an individual customer waiting in line, and $c_{s}>0$ be the cost of sensing (incurred by each customer who chooses to sense, regardless of the consequences of his action). Since all customers are identical, and each one arriving at the system is eventually attained to service, neither the reward from service nor the time spent in service is relevant. Of course, the state of the system, including the length of the queue and the status of the servers, is unobservable as mentioned, and unknown to the customers at the time they make their decisions. We assume the system is not overloaded (i.e., $\rho<\varphi$) and that all customers act to reduce their expected cost to minimum. Denote $C_{S}(p)$ and $C_{N}(p)$ the expected cost of an individual who chooses to sense and an individual who chooses not to sense, respectively, given that the others' probability of sensing is $p$.
\begin{equation}\begin{cases}
 	C_{N}(p) = \frac{c_{w}}{\mu}\e\left[L(p)\right] \:, \\
	C_{S}(p) = c_{s} + \pr(Y=1) \cdot \frac{c_{w}}{\mu} \e\left[L(p)\mid Y=1\right] \:,
\end{cases}
\label{CostFunc}
\end{equation}
where $L(p)$ is a random variable representing the queue length (including the customer in service) upon arrival to the system.

Prior to discussion of equilibrium strategies we assert some attributes of $\e\left[L(p)\mid Y=0\right]$ which appear to be essential in this context. 
%The claim that this function is non-increasing in $p$ may seem obvious at first glance, as the effective utilization of the queue, $\hat{\rho}(p,\rho)$, defined in (\ref{EffectiveUtil}), is monotone decreasing in $p$. Subsequent glances, however,

\begin{proposition}
The function $\e\left[L(p)\mid Y=0\right]$ is continuous and monotone non-increasing in $p$. \label{MonotonicityProp}
\end{proposition}

\begin{proof}
Proving the continuity of $\e\left[L(p)\mid Y=0\right]$ is immediate, as, referring to (\ref{OMLossProb}), (\ref{P00PlusP01}) and (\ref{Forms}),
\[ \e\left[L(p)\mid Y=0\right] = \frac{1}{\Pr(Y=0)}\sum\limits_{i=0}^{\infty} i P_{i, 0} = (1+p\rho) \sum\limits_{i=0}^{\infty} i P_{i, 0} \:,\]
which is a countable sum of compositions of continuous functions in $p \in [0,1]$.

In order to prove monotonicity, we examine the transitions between states in two systems, $\Omega := \lbrace S_Q, S_L \rbrace$ and $\Omega' := \lbrace S'_Q, S'_L \rbrace$, under the same sequence of events. Systems $\Omega$ and $\Omega'$ are identical except that in $\Omega$ the sensing probability is $p$, as opposed to $\Omega'$, where the sensing probability is $p'$, and $p < p'$.

Denote by $(X(t),Y(t))$ and $(X'(t),Y'(t))$ the states at time $t$ of systems $\Omega$ and $\Omega'$ respectively. Since that for all $p \in [0,1]$ the state $(0,0)$ in the Markov chain is recurrent, we can assume without loss of generality, that at time $t=0$, 
\[(X(0),Y(0)) = (X'(0),Y'(0)) = (0,0)\:.\] 
Showing that 
\begin{equation}
\forall t \in [0,\infty) : \e[X(t) \mid Y(t) = 0] \geq \e[X'(t) \mid Y'(t) = 0] \label{SuffArg4.1}
\end{equation}
will complete the proof.

We begin by attaching three variables to each customer: Let $\lbrace{ (T_i, \tau_i, u_i) \rbrace}_{i \in \mathbb{N} }$ represent the {\it arrival time}, {\it service duration} and {\it sensing aversion} of the $i$-th customer respectively, and for all $i \in \mathbb{N}$: 
\[T_{i+1} - T_i \sim \expdist(\Lambda) \:, 
\quad \tau_i \sim \expdist(\mu) \:,
\quad u_i \sim \U[0,1] \:.\]
Each customer arrives to both systems simultaneously. Customer $i$ arriving at $\Omega$ senses if and only if $u_i \leq p$, and similarly, arriving at $\Omega'$ he/she senses if and only if $u_i \leq p'$. This ensures that the sensing probability is $p$ in system $\Omega$ and $p'$ in system $\Omega'$, and as a fact, implies that customers who sense in $\Omega$ also sense in $\Omega'$. Note that the value $u_i$ is only relevant when 
$Y(T_i)=0$ or $Y'(T_i)=0$.

We assign each customer one of three types, based on the values of their sensing aversion: Customer $i$ will be assigned
\begin{itemize}
\item {\it type-L} (stands for ``Low'') if $u_i \in [0, p]$,
\item {\it type-M} (stands for ``Medium'') if $u_i \in (p, p']$,
\item {\it type-H} (stands for ``High'') if $u_i \in (p',1]$.
\end{itemize}
We reiterate that one's type is only significant if $S_L$ or $S'_L$ are empty by the time of customers' arrival.
By definition, upon arrival, an H-type customer joins both $S_Q$ and $S'_Q$, an M-type customer joins $S_Q$ but senses $S'_L$, whereas an L-type customer senses both $S_L$ and $S'_L$.

Without loss of generality, we modify the service regime as follows: 
\begin{enumerate}[label=(\roman*)]
\item\label{Assump1} Arriving at $\Omega$ ($\Omega'$) when $S_L$ ($S'_L$) is busy, customer $i$ preempts the customer in service in $S_L$ ($S'_L$) with no regard to type, and the preempted customer is routed to continue the service in $S_Q$ ($S'_Q$). Arriving at $\Omega$ ($\Omega'$) when $S_L$ ($S'_L$) is empty, customer-$i$'s actions are followed by type.
\item\label{Assump2} Subsystem $S_Q$ ($S'_Q$) is a preemptive resume LCFS queue, meaning that customers are served following a preemptive LCFS discipline, and the preempted service will be resumed from the point it is stopped.
\end{enumerate}

\begin{lemma}
Assumptions {\rm \ref{Assump1}} and {\rm \ref{Assump2}} do not affect the stationary probabilities of the systems. \label{WlogAssump}
\end{lemma}

We shall show that Lemma \ref{WlogAssump} holds for system $\Omega$ and the proof for $\Omega'$ is identical.

Let $i$ and $i+1$ be a successive pair of customers and suppose that customer $i+1$ preempts customer $i$ in subsystem $S_L$. Denote $\Delta_{i,i+1} := T_{i+1}-T_i$ the time difference between their arrivals. Then, as a result of the memoryless property of the exponential distribution, the service duration of customer $i+1$ (i.e., $\tau_{i+1}$) and the residual service of customer $i$ (i.e., $\tau_i-\Delta_{i,i+1} \mid \tau_i>\Delta_{i,i+1}$) are independent and identically distributed. This incident of preemption is equivalent to the joining of the new comer to  subsystem $S_Q$ when $S_L$ is busy. Hence, assumptions \ref{Assump1} does not influence the transition probabilities and the stationary probabilities remain as before.

The validity of assumption (ii) can be explained by the fact that in a work-conserving preemptive resume system with exponential i.i.d services duration, as sustains in $S_Q$, the length of the queue is independent of the service regime. Consequently, assumptions \ref{Assump1} and (ii) do not restrict the generality of the model.
\end{proof}

Exploiting assumptions \ref{Assump1} and \ref{Assump2} we immediately achieve several properties that will be later used in the proof:

\begin{lemma}
Under assumptions {\rm \ref{Assump1}} and {\rm\ref{Assump2}}, the following arguments hold:

\begin{enumerate}[label=(\alph*)]
\rm \item\label{Prop1} \it At any moment, if $S_L$ ($S'_L$) is not idle, then the last customer to arrive until that moment is in $S_L$ ($S'_L$).
\rm \item\label{Prop2} \it All customers begin service at the moment of their arrival, whether they sense or not.
\rm \item\label{Prop3} \it Customers joining $S_L$ upon their arrival,  attend $S'_L$ as well.
\rm \item\label{Prop4} \it Customers joining $S'_Q$ upon their arrival, attend $S_Q$ as well.% (the {\it modus tollens} form of \ref{Prop3}).
\rm \item\label{Prop5} \it The sojourn time of customer $i$ in $S'_Q$ is no greater then the sojourn time of $i$ in $S_Q$.% (from \ref{Prop4}, customers who arrive at $S'_Q$ after $i$, simultaneously arrive at $S_Q$).

\end{enumerate}
\end{lemma}

\begin{proof}
\begin{enumerate}[label=(\alph*)]
\item From assumption \ref{Assump1}, in a certain time $t$, the only scenario in which the last customer to arrive at $\Omega$ does not join $S_L$, is when he/she is not of type 'L' and $S_L$ is idle at the moment of his/her arrival. Hence, $S_L$ stays idle at time $t$. The proof for $\Omega'$ is similar.
\item At the moment of their arrival, costumers either begin service immediately in $S_L$, or, by assumption \ref{Assump2} join the head of the line in $S_Q$. The proof for $\Omega'$ is similar.
\item Recall that at time $t=0$ both $S_L$ and $S'_L$ are empty. Only upon an arrival of an L-type customer will the state of $S_L$ alter. Arriving at $\Omega'$, an L-type customer joins $S'_L$, regardless of the server's state. Suppose the last customer has joined both $S_L$ and $S'_L$. By assumption \ref{Assump1}, this tagged customer can either complete service in $S_L$ and $S'_L$ simultaneously (so $S_L$ and $S'_L$ become empty) or be preempted in the two subsystems by the next customer to come. As for the latter case, it holds that the preempting customer joins both $S_L$ and $S'_L$. Thus, it follows by induction that customers who join $S_L$ also join $S'_L$.
\item This property is immediately achieved as the {\it modus tollens} form of property \ref{Prop3}.
\item It results from assumption \ref{Assump2} that the sojourn time of each customers depends on future arrivals to the queue. Combining this with property \ref{Prop4} we deduce \ref{Prop5}. 
\end{enumerate}
\end{proof}

With property \ref{Prop3} and the simultaneousness of occurrences we get:
\[ \forall t  \in [0, \infty): \lbrace{ Y(t)=1 \rbrace} \Rightarrow \lbrace{ Y'(t)=1 \rbrace} \:, \]
or, in an analogous fashion:
\begin{equation}
\forall t  \in [0, \infty): \lbrace{ Y'(t)=0 \rbrace} \Rightarrow \lbrace{ Y(t)=0 \rbrace} \:.\label{BusyTimesComp}
\end{equation}
Moreover, from properties \ref{Prop4} and \ref{Prop5}, we see that at an arbitrary point in time, each customer in $S'_Q$, must as well linger in $S_Q$, not leaving $\Omega$ before leaving $\Omega'$. Therefore, 
\begin{equation}
\forall t \in [0, \infty):  X(t) \geq X'(t) \:, \label{StDomination}
\end{equation}
which implies that the process representing the number of customers in $S_Q$ over time stochastically dominates the one that represents the number of customers in $S'_Q$.

For simplicity, we denote $(X(t), Y(t))$ by $(X,Y)$, and $(X'(t),Y'(t))$ by $(X', Y')$ (all equations are to be understood at an arbitrary time sample). On utilizing (\ref{StDomination}), we get
\[ \e[X' \mid Y' = 0] \leq \e[X \mid Y' = 0] \:.\]
To prove our claim (\ref{SuffArg4.1}) it suffices to prove:
\begin{equation}
\e[X \mid Y' = 0] \leq \e[X \mid Y = 0] \:. \label{SufArg}
\end{equation}

Denote $i$ the last customer that arrived by time $t$, and let \[A(t):= \lbrace \mbox{$i$ joined $S_Q$ and $T_i + \tau_i > t$} \rbrace\]
express the event ``$i$ joined $S_Q$ and had not left until $t$''. Because of property \ref{Prop2}, this is possible if and only if $i$ was still in service in $S_Q$ by time $t$. By definition,
\begin{equation}
A(t) \Rightarrow \lbrace Y(t)=0 \rbrace \:. \label{ZCausesY0}
\end{equation}
Clearly, given that $i$ has not left $\Omega$ by time $t$, the residual service of customer $i$ at $t$ is exponential with parameter $\mu$. Thus, we can assume w.l.o.g that $T_i$ occurred a moment before $t$ and $A(t)$ can be rewritten as the event when a new busy period in $S_Q$ began right before $t$ (i.e., $t = T_i^+ := T_i +\varepsilon$, where $\varepsilon$ is a small positive infinitesimal quantity).

Recall that, by property \ref{Prop1}, if there is a customer in $S_L$ at time $t$, then it must be $i$ (the last customer arrived). So, if $t \in \mathbb{R}$ satisfies $Y(t)=0$ and $Y'(t)=1$, customer $i$ joined $S_Q$ at the same time beginning service in $S'_L$, and, together with property \ref{Prop2}, had not left the system before $t$. Hence,
\begin{equation}
\lbrace \lbrace Y'(t)=1 \rbrace \wedge \lbrace Y(t)=0 \rbrace \rbrace \Rightarrow A(t) \:. \label{Y'1&Y0ImplZ}
\end{equation}

\begin{lemma}
Conditioned on $A(t)$, $X(t)$ and $Y'(t)$ are independent random variables.
\label{CondIndep}
\end{lemma}
\begin{proof}
Denote $T_n^+$ the moment after customer-$n$'s arrival. We shall show by induction that $\forall n \in \mathbb{N}$, $ X(T_n^+)$ and $Y'(T_n^+)$ are conditionally independent given $A(T_n^+)$.

Note that as $A(T_n^+)$ occurs, the values of $Y'(T_n^+)$ can be specified one to one by customer-$n$'s actions: 
\begin{equation}
\lbrace Y'(T_n^+) \mid A(T_n^+) \rbrace = \begin{cases} 0, \mbox{ iff $n$ joins $S'_Q$}; \\ 1, \mbox{ iff $n$ joins $S'_L$}. \end{cases}\label{Y'(Tn+)|A(Tn+)}
 \end{equation}

Presume that $A(T_n^+)$ is satisfied. Having that $n$ joined $S_Q$ means that $n$ is not of type-L, and, by (\ref{ZCausesY0}), $Y(T_n^+)=0$. Define $T_i^- := T_i -\varepsilon$, where $\varepsilon$ is a small positive infinitesimal quantity, the moment before $i$'s arrival. Regarding $n$'s arrival at $\Omega'$, there are two possibilities:
\begin{itemize}
\item Upon $n$'s arrival, $S'_L$ was empty (i.e., $Y'(T_n^-)=0$).
\item Upon $n$'s arrival, $S'_L$ was busy (i.e., $Y'(T_n^-)=1$).
\end{itemize}

To the extent that $Y'(T_n^-)=0$, $n$'s action is determined by type (M or H), which is chosen randomly and independently, thus (\ref{Y'(Tn+)|A(Tn+)}) can be rephrased to
\[
\lbrace Y'(T_n^+) \mid A(T_n^+) \rbrace = \begin{cases} 0, \mbox{ iff $n$ is of type-H}; \\ 1, \mbox{ iff $n$ is of type-M}. \end{cases}
\]
and $X(T_n^+)$ and $Y'(T_n^+)$ are independent.
